Testing and Isolation Efficacy:\\Insights from a Simple Epidemic Model \thanks{Grants or other notes about the article that should go on the front page should be placed here. General acknowledgments should be placed at the end of the article.}

### 2021-07-21 methods.tex
newlines to improve typsetting of table

\begin{table}[htp]
\centering
%%\begin{tabular}{|c|L{2in}cc|} \hline
%% making use of ragged2e and array packages:
{\RaggedRight
\begin{tabular}{ c | m{6cm} | c | c }
  \textbf{Symbol} & \textbf{Description} & \textbf{Unit} & \textbf{Value} \\ \hline
  $N$     & Total population size & people & $10^6$ \\ \hline
  $\omega$  & Rate of test return, i.e., rate of onward flow from ``waiting'' to ``confirmed'' or ``untested'' compartments  & 1/day & - \\ \hline
  $\gamma$ & Recovery rate & 1/day & 1/6 \\ \hline 
  $\rho$   & \percap testing intensity & 1/day & - \\ \hline 
  $\theta\_w$ & Isolation efficacy (reduction of the transmission probability) for ``waiting'' individuals & - & - \\ \hline
  $\theta\_c$ & Isolation efficacy for ``confirmed positive'' individuals & - & -  \\ \hline
  $\beta$ & Transmission rate & 1/day & 0.5 \\ \hline
  $\Lambda$ & Force of infection & 1/day & - \\ \hline
  $p_S$ & Probability of positive tests for $S$ ($= 1-\textrm{specificity}$) & - & 0 \\ \hline
  $p_I$ & Probability of positive tests for $I$ ($= \textrm{sensitivity}$) & - & 1 \\ \hline
  $p_R$ & Probability of positive tests for $R$ ($= 1-\textrm{specificity}$) & - & 0.5 \\ \hline
  $w_S, w_I, w_R$ & Relative testing weights & - &
  \begin{minipage}[t]{0.21\columnwidth}%
    Random:~$\{1,1,1\}$ \\ Targeted:~$\{0.3,1,1\}$
  \end{minipage} \\
  %%\hline
\end{tabular}
} % end \RaggedRight
\caption{\label{tab:params}Parameters of the model specified  by the flow chart in \fref{fig:flowchart} and equations~\eqref{model}.}
\end{table}

>>>>

\begin{table}[htp]
\centering
%%\begin{tabular}{|c|L{2in}cc|} \hline
%% making use of ragged2e and array packages:
{\RaggedRight
\begin{tabular}{ c | m{6cm} | c | c }
  \textbf{Symbol} & \textbf{Description} & \textbf{Unit} & \textbf{Value} \\ \hline
  $N$     & Total population size & people & $10^6$ \\ \hline
  $\omega$  & Rate of test return, i.e., rate of onward flow from ``waiting'' to ``confirmed'' or ``untested'' compartments  & 1/day & - \\ \hline
  $\gamma$ & Recovery rate & 1/day & 1/6 \\ \hline 
  $\rho$   & \percap testing intensity & 1/day & - \\ \hline 
  $\theta\_w$ & Isolation efficacy (reduction of the transmission probability) for ``waiting'' individuals & - & - \\ \hline
  $\theta\_c$ & Isolation efficacy for ``confirmed positive'' individuals & - & -  \\ \hline
  $\beta$ & Transmission rate & 1/day & 0.5 \\ \hline
  $\Lambda$ & Force of infection & 1/day & - \\ \hline
  $p_S$ & Probability of positive tests for $S$\newline ($= 1-\textrm{specificity}$) & - & 0 \\ \hline
  $p_I$ & Probability of positive tests for $I$\newline ($= \textrm{sensitivity}$) & - & 1 \\ \hline
  $p_R$ & Probability of positive tests for $R$\newline ($= 1-\textrm{specificity}$) & - & 0.5 \\ \hline
  $w_S, w_I, w_R$ & Relative testing weights & - &
  \begin{minipage}[t]{0.21\columnwidth}%
    Random:~$\{1,1,1\}$ \\ Targeted:~$\{0.3,1,1\}$
  \end{minipage} \\
  %%\hline
\end{tabular}
} % end \RaggedRight
\caption{\label{tab:params}Parameters of the model specified  by the flow chart in \fref{fig:flowchart} and equations~\eqref{model}.}
\end{table}
